Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
Change wording for better margins.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports}
Some pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments}
Our proposed censorship environments are informed
by real-world censors.
What other representative environments
should be tested?

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports}
Some of Tor's pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments}
Our proposed censorship simulation is informed
by real-world censors.
What other representative environments
should be tested?
